---
title: "Test Answers"
format: html
editor: visual
---

### Load packages

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
```

### 1. Read csv and clean column names and print column names

```{r, message=FALSE, warning=FALSE}
"10_Property_stolen_and_recovered.csv" %>% 
  read_csv() %>% 
  clean_names() -> df1

print(colnames(df1))
```

### 2. Rename area_name to state_ut

```{r}
df1 %>% 
  rename("state_ut" = "area_name") -> df2
```

### 3. How many state_ut are there

```{r}
df2 %>% 
  pull(state_ut) %>%
  unique() %>%
  length()
```

### 4. How many crime groups are there and what are those

```{r}
df2 %>% pull(group_name) %>% unique() 
df2 %>% pull(group_name) %>% unique() %>% length()
```

### 5. In group_name what is "Total Property" and what should we do? ====

Ans. "Total Property" is the sum of other groups (Burglary, Criminal Breach of Trust, Robbery, Theft and Other).

Since "Total Property" is not a crime but a total of all other crimes lets filter it out

```{r}
df2 %>% 
  filter(group_name != "Total Property") -> df3
```

### 6. What is the total no of property stolen cases and total value - All india

```{r}
df3 %>% 
  pull(cases_property_stolen) %>% 
  sum(na.rm = T) -> total_cases

df3 %>% 
  pull(value_of_property_stolen) %>% 
  sum(na.rm = T) -> total_value
```

### 7. What is the total no of property stolen cases and total value - All india - Year wise. (With table and plot)

```{r}
df3 %>% 
  group_by(year) %>% 
  summarise(total_cases = sum(cases_property_stolen, na.rm = T),
            total_value = sum(value_of_property_stolen, na.rm = T)) -> year_wise_summary

year_wise_summary %>% 
  mutate(total_cases = total_cases/100000) %>% 
  ggplot(aes(x = year, 
             y = total_cases)) +
  geom_col(fill = "orange") +
  scale_x_continuous(breaks = c(2000:2011)) +
  labs(title = "Total No of theft cases",
       subtitle = "2001 to 2010",
       x = "Year",
       y = "Total No of cases (Lakh)") +
  theme_light()
```

```{r}
year_wise_summary %>% 
  mutate(total_value = total_value/10000000000) %>% 
  ggplot(aes(x = year, 
             y = total_value)) +
  geom_col(fill = "steelblue") +
  scale_x_continuous(breaks = c(2000:2011)) +
  labs(title = "Total value of Theft cases",
       subtitle = "2001 to 2010",
       x = "Year",
       y = "Total value of cases (000'cr)") +
  theme_light()
```

### 8. States with no of cases, Plot the same

```{r}
df3 %>% 
  group_by(state_ut) %>% 
  summarise(total_cases = sum(cases_property_stolen, na.rm = T)) %>% 
  mutate(total_cases = total_cases/100000) %>% 
  mutate(state_ut = state_ut %>% fct_reorder(total_cases)) %>% 
  ggplot(aes(x = state_ut,
             y = total_cases)) +
  geom_col(fill = "red") +
  coord_flip() +
  theme_minimal() +
  labs(title = "State with no. of stolen cases",
       subtitle = "2001 to 2010",
       y = "Total No of cases (Lakh)",
       x = NULL)
```

### 9. Correlation plot between Stolen and recover

```{r}
df3 %>% 
  mutate(year = year %>% factor()) %>% 
  ggplot(aes(x = cases_property_stolen,
             y = cases_property_recovered,
             color = year)) +
  geom_point() +
  scale_x_continuous(breaks = seq(0,100000, 5000)) +
  scale_y_continuous(breaks = seq(0,100000, 1000)) +
  labs(title = "Correlation between Stolen and Recovered Property",
       subtitle = "2001:2010",
       x = "Stolen",
       y = "Recovered",
       color = NULL)
```

### 10. No of Stolen and Recover cases year wise

```{r}
df3 %>% 
  pivot_longer(c("cases_property_stolen", "cases_property_recovered"),
               names_to = "type",
               values_to = "no_cases") %>% 
  mutate(year = year %>% factor()) %>% 
  group_by(year, type) %>% 
  summarise(count = sum(no_cases, na.rm = T)) %>% 
  mutate(count = count/100000) %>% 
  ggplot(aes(x = year, 
             y = count,
             fill = type)) +
  geom_col() +
  scale_fill_manual(values = c("darkgreen", "orange")) +
  labs(title = "No of Stolen and Recover cases year wise",
       subtitle = "2001-2010",
       x = NULL,
       y = "Total No of cases (Lakh)",
       fill = NULL) +
  theme_linedraw()
```
